Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2

### 2019-02-14 Thesis_Latex/FinalReport/FinalReport.tex
update final report

\documentclass[conference,11pt]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{stfloats}
\usepackage{midfloat}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{lipsum}
\usepackage[utf8x]{inputenc}
\usepackage{float}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{caption,subcaption}
%\usepackage{amsmath}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[font={small,it}]{caption}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{standalone}
\usepackage{balance}
%\usepackage{isomath}
%\renewcommand{\vec}{\mathbfit}
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{\mathit{#1}}}}

@@

\title{Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2}
\author{
	\IEEEauthorblockN{Alberto Franco}
	\IEEEauthorblockA{Department of Information Engineering,\\ Università degli Studi di Padova, Italy\\		 \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}\\
	\href{mailto:alberto.franco@ua.pt}{alberto.franco@ua.pt}}
	}

\begin{document}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
	This report presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles. The main task is to study and implement a motion planning and execution framework in order to make ATLASCAR2 coexist with other moving obstacle vehicles by avoiding collision and overtake them when necessary and possible. The proposed techniques, based on the Model Predictive Control paradigm, solve optimization problems formulated in terms of cost minimization under constraints. Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation.
\end{abstract}

\section{Introduction}
In robotic research, the problem of navigation is among the most important. Basically, all autonomous mobile robots need some kind of navigation abilities to perform, localization, motion planning and guidance \cite{skoda}.
In the present context, we focus on navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC} \cite{NONMPC}. The desired paths have to fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}. Moreover, the paths can be also defined in terms of specifications; for example, short or smooth paths are usually more desirable than long and curved ones in very dynamic environments \cite{archi}. Beyond the path planning, the navigation problem also involves reacting to changes of the environment model. Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC} \cite{autoMPC}. Though these two topics have been well researched, currently, there is no definitive solution to manage the navigation problem within cluttered dynamic environments. In the literature many collision avoidance methods have been developed for wheeled mobile robots; they can be grouped in four categories: graph-search based methods \cite{RRT}, artificial potential field based methods \cite{potential}, meta-heuristic based methods \cite{meta-heuristic} and mathematical optimization based methods \cite{borelli2}.
The latter are very interesting because they offer a systematic and precise way to take vehicle dynamics and safety constraints into account and can produce optimal control inputs. This approach can be used in an closed-loop with a feedback controller for a stronger solution regarding to the Model Predictive Control (MPC). A prior research about obstacle avoidance using MPC in UGVs is described in \cite{borelli} while the applications of nonlinear MPC to ground vehicles is described and evaluated in \cite{nonlinearmpc}.
\section{Context and Proposed Solution}

@@

\begin{figure*}[!b]
	\centering
	\includegraphics[width=1\textwidth]{./figure/lane_following_AMPC.pdf}
	\caption{Overall procedure scheme lane following.}
	\label{fig:scheme_lane_following}
\end{figure*}
\section{Conclusions and Future Work}
This report proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control. The first component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle. This system updates both the predictive model and the mixed input/output constraints at each control interval. The vehicle is also able to brake in order to prevent collisions against closest obstacles. Instead, in the second scheme  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.  The flexibility of the concepts used in the algorithms allows a multitude of refinements and extensions to this work. The future work includes the combination of these two control strategies in a way that they can operate simultaneously. Next expected steps include the migration to ROS-Gazebo simulation environment and, later on, the usage of real data collected on board the ATLASCAR2 and, ultimately, test it in a real autonomous driving scenario.

@@

	\bibitem{curvature}Danwei Wang, Feng Qi, "Trajectory planning for a four-wheel-steering vehicle," 2001 International Conference on Robotics and Automation, Seoul, Korea, 2001
\end{thebibliography}

>>>>

\documentclass[conference,11pt]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{multirow}
\usepackage{multicol}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage{listings}
\usepackage{stfloats}
\usepackage{midfloat}
\usepackage{color}
\usepackage[table]{xcolor}
\usepackage{lipsum}
\usepackage[utf8x]{inputenc}
\usepackage{float}
\usepackage{bbm}
\usepackage{graphicx}
\usepackage{caption,subcaption}
%\usepackage{amsmath}
\usepackage{amsmath,amsfonts,amssymb}
\usepackage[font={small,it}]{caption}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{standalone}
\usepackage{balance}
%\usepackage{isomath}
%\renewcommand{\vec}{\mathbfit}
\renewcommand{\vec}[1]{\ensuremath{\boldsymbol{\mathit{#1}}}}

@@

\title{Local Path Planning with Moving Obstacle Avoidance based on adaptive MPC in ATLASCAR2}
\author{
	\IEEEauthorblockN{Alberto Franco}
	\IEEEauthorblockA{Department of Information Engineering,\\ Università degli Studi di Padova, Italy\\		 \href{mailto:alberto.franco.3@studenti.unipd.it}{alberto.franco.3@studenti.unipd.it}\\
	\href{mailto:alberto.franco@ua.pt}{alberto.franco@ua.pt}}
	}
\usepackage{pdfpages}
\begin{document}
\includepdf[page=-]{./coverpage/coverpage.pdf}
\maketitle
\thispagestyle{plain}
\pagestyle{plain}
\begin{abstract}
	This report presents two different strategies for a self-driving car short-term path planning among multiple moving obstacles. The main task is to study and implement a motion planning and execution framework in order to make ATLASCAR2 coexist with other moving obstacle vehicles by avoiding collision and overtake them when necessary and possible. The proposed techniques, based on the Model Predictive Control paradigm, solve optimization problems formulated in terms of cost minimization under constraints. Simulation results demonstrate and verify the feasibility and the usefulness of methods considering different scenarios, opening space for real scenario implementation.
\end{abstract}
\section{Introduction}
In robotic research, the problem of navigation is among the most important. Basically, all autonomous mobile robots need some kind of navigation abilities to perform, localization, motion planning and guidance \cite{skoda}.
In the present context, we focus on navigation as a process of planning a path of a mobile robot from its current position to a desired goal location, following the planned path, and avoiding any discovered obstacles along the way \cite{fuzzyMPC} \cite{NONMPC}. The desired paths have to fulfill several conditions to ensure safety and feasibility of the navigation \cite{safety}. Moreover, the paths can be also defined in terms of specifications; for example, short or smooth paths are usually more desirable than long and curved ones in very dynamic environments \cite{archi}. Beyond the path planning, the navigation problem also involves reacting to changes of the environment model. Robots are required to move towards the target in a short time and avoid either static or dynamic obstacles observed by their sensors, which involves efficient path planning and valid obstacle avoidance \cite{MMPC} \cite{autoMPC}. Though these two topics have been well researched, currently, there is no definitive solution to manage the navigation problem within cluttered dynamic environments. In the literature many collision avoidance methods have been developed for wheeled mobile robots; they can be grouped in four categories: graph-search based methods \cite{RRT}, artificial potential field based methods \cite{potential}, meta-heuristic based methods \cite{meta-heuristic} and mathematical optimization based methods \cite{borelli2}.
The latter are very interesting because they offer a systematic and precise way to take vehicle dynamics and safety constraints into account and can produce optimal control inputs. This approach can be used in an closed-loop with a feedback controller for a stronger solution regarding to the Model Predictive Control (MPC). A prior research about obstacle avoidance using MPC in UGVs is described in \cite{borelli} while the applications of nonlinear MPC to ground vehicles is described and evaluated in \cite{nonlinearmpc}.
\section{Context and Proposed Solution}

@@

\begin{figure*}[!b]
	\centering
	\includegraphics[width=1\textwidth]{./figure/lane_following_AMPC.pdf}
	\caption{Overall procedure scheme lane following.}
	\label{fig:scheme_lane_following}
\end{figure*}
\section{Conclusions and Future Work}
This report proposes two advanced methods for short term motion planning of an autonomous car based on adaptive Model Predictive Control. The first component is an obstacle avoidance system that moves the vehicle around different moving obstacles in the lane using throttle and steering angle. This system updates both the predictive model and the mixed input/output constraints at each control interval. The vehicle is also able to brake in order to prevent collisions against closest obstacles. Instead, in the second scheme  we have developed a lane following system that keeps the ATLASCAR2 traveling along the centerline of the lanes on the road by adjusting the front steering angle of the car.  The flexibility of the concepts used in the algorithms allows a multitude of refinements and extensions to this work. The future work includes the combination of these two control strategies in a way that they can operate simultaneously. In order to achieve this objective we have started to simulate a trajectory tracking framework using a slight modification of the linearized tracking error model in \cite{error_model}. Next expected steps include the migration to ROS-Gazebo simulation environment and, later on, the usage of real data collected on board the ATLASCAR2 and, ultimately, test it in a real autonomous driving scenario.

@@

	\bibitem{curvature}Danwei Wang, Feng Qi, "Trajectory planning for a four-wheel-steering vehicle," 2001 International Conference on Robotics and Automation, Seoul, Korea, 2001

	\bibitem{error_model}H. Yang, M. Guo, Y. Xia and L. Cheng, "Trajectory tracking for wheeled mobile robots via model predictive control with softening constraints," in IET Control Theory \& Applications, vol. 12, no. 2, pp. 206-214, 30 1 2018.
\end{thebibliography}
